Code Clones: To refactor or not to refactor?

### 2020-05-09 ase/paper.tex
Updates from Overleaf

We built a tool that can automatically apply refactorings to 28\% of the clones in our corpus using the ``Extract Method'' refactoring technique. It measured the change in four maintainability metrics to determine the impact of each refactoring on system maintainability. We found that the most prominent factor influencing maintainability is the size of the clone. We found that the threshold lies at a clone volume of 63 tokens for all clone instances combined for system maintainability to increase after refactoring the clone.

@@

We also limited our scope by choosing a set of four metrics. However, software maintainability depends on more factors and can be measured by more metrics. By taking more metrics into account, we can give a better indication whether the maintainability improves after refactoring. For instance, we think that module coupling \cite{briand1999unified,heitlager2007practical} is an important metric to be considered when refactoring clones. In future work we will investigate other groups of maintainability metrics to broaden the understanding of factors influencing the desirability of a refactoring.

>>>>

We built a tool that can automatically apply refactorings to 28\% of the clones in our corpus using the ``Extract Method'' refactoring technique. We measured the change in four maintainability metrics to determine the impact of each refactoring on system maintainability. We found that the most prominent factor influencing maintainability is the size of the clone. We found that the threshold lies at a clone volume of 63 tokens for all clone instances combined for system maintainability to increase after refactoring the clone.

@@

Our scope is currently limited to a set of four metrics. However, software maintainability depends on more factors and can be measured by more metrics. By taking more metrics into account, we can give a better indication whether the maintainability improves after refactoring. For instance, we think that module coupling \cite{briand1999unified,heitlager2007practical} is an important metric to be considered when refactoring clones. In future work we will investigate other groups of maintainability metrics to broaden the understanding of factors influencing the desirability of a refactoring.
